My title

### 2023-03-13 outputs/paper/paper.qmd
data cleaning for sex

```{r}

>>>>

ggplot(subset_data_freq, aes(x = income, y = freq, fill = edu_year)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_x_discrete(labels = c("LT $1000","", "$1000 TO 2999","", "$3000 TO 3999","",
                              "$4000 TO 4999","", "$5000 TO 5999","","$6000 TO 6999", "",
                              "$7000 TO 7999","","$8000 TO 9999","","$10000 - 14999","",
                              "$15000 - 19999","","$20000 - 24999","","$25000 OR MORE")) +
  labs(y = "Numbers of people", title = "Numbers of people of Income by race") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
